### 2009-02-02 articles/2009/geoinformatics/article.tex
Added author background
git-svn-id: https://svn.osgeo.org/qgis/trunk@10089 c8812cc2-4d05-0410-92ff-de0c093fc19c

An example using this approach is the QGIS mapserver project
(\url{http://karlinapp.ethz.ch}) that provides a WMS
compatible mapserver on top of the QGIS core library. This software has no 
graphical user interface. It is a FastCGI application that waits until called
by a webserver. It parses the request parameters and uses QGIS to render a map
into an offscreen buffer. The content is then returned as binary image back to
the client.

@@

Otto Dassau <dassau@nature-consult.de>
\\Gary Sherman <sherman@mrcc.com>
\\Tim Sutton <tim@linfiniti.com>: Tim runs a consultancy business in Gauteng,
South africa where he provides commercial support and development services for
QGIS and other FOSS GIS software.
\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>
\\Paolo Cavallini <cavallini@faunalia.it>

>>>>

An example using this approach is the QGIS mapserver project
(\url{http://karlinapp.ethz.ch/qgis\_wms}) that provides a WMS
compatible mapserver on top of the QGIS core library. This software has no 
graphical user interface. It is a FastCGI application that waits until called
by a webserver. It parses the request parameters and uses QGIS to render a map
into an offscreen buffer. The content is then returned as binary image back to
the client.

@@

Otto Dassau <dassau@nature-consult.de>
\\Gary Sherman <sherman@mrcc.com>
\\Tim Sutton <tim@linfiniti.com>: Tim runs a consultancy business in Gauteng,
South africa where he provides commercial support and development services for
QGIS and other FOSS GIS software.
\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>: Marco lives in Zurich, Switzerland. He works for the Institute of Cartography, ETH Zurich and for his company that provides programming and consulting services for FOSS GIS software.
\\Paolo Cavallini <cavallini@faunalia.it>
